Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-01 paper/ms.tex
update manuscript

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals, and the error-bar shows the median uncertainty for the
    black points.  The gray line shows the median model corresponding
    to the combined TESS and ground-based transit fit
    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
    0.36m; gray points are binned to 10-minute intervals.  Models show
    $2\sigma$ lower limits on the transit depths in the Cousins-R and
    Johnson-B bandpasses used to rule out specific false positive
    scenarios (see Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
    {\bf SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments.} Star A ($\Delta T=4.7$,
    $2.3''$ west) is detected in the autocorrelation function, in
    addition to being a resolved Gaia source.  It is co-moving with
    \tn, and its parallax and on-sky position imply that it is
    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

@@

{\bf Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:soar}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities of \tn.}
		{\it Top:} RV measurements, with best-fit instrument offsets
    and jitter terms included.  The expected scatter from starspots
    based on $v\sin i$ and the photometric modulation amplitude is of
    order 300m$\,$s$^{-1}$.
		{\it Bottom:}
    RV measurements phased to the orbital ephemeris of \pn.  The
    planet is not detected.  The black line shows a circular
    Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:rvs}
	}
\end{figure}

@@

{\bf George TODO: please describe the formal secondary line search in
more depth in this paragraph} We searched for secondary lines in the
CHIRON spectra by cross-correlating against a {\bf template of some
kind}.  This rules out lines with flux ratios of $\approx 2\%$, if the
lines are well-separated in velocity.  To derive the star's physical
parameters, we cross-correlated the template against {\bf something},
and used the {\bf \texttt{nameofcode}}.  We measured the radial
velocities through a least-squares deconvolution of the observed
spectra against the same synthetic template.  The resulting velocities
are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.

@@

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, {\bf
Rafael TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:rvs}.

@@

Many of the exposures were taken in average or poor seeing conditions,
when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due to
uncorrected fiber-to-fiber cross-contamination.  For
analysis purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:rvs}.

@@

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit, we assumed a restrictive prior on the period and
time of periapse, using the known ephemeris from the transit.  We then
fitted for the semi-amplitude, instrument offsets, and jitter
parameters.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:rvs}.

>>>>

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements with the local spot-induced variation removed as
    described in Section~\ref{subsec:planet}.  Black points are binned
    to 6-minute intervals, and the error-bar shows the median
    uncertainty for the black points.  The gray line shows the median
    model corresponding to the combined TESS and ground-based transit
    fit (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m; gray points are binned to
    10-minute intervals.  Models show $2\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

@@

{\bf Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f6.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
		SOAR HRCam contrast limits derived from point-source
		injection-recovery experiments. A companion dubbed Star A ($\Delta T=4.7$,
	$2.3''$ west) is detected in the autocorrelation function,
	and is also a resolved Gaia source.  It is co-moving with
	\tn, and its parallax and on-sky position imply that it is
	physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		{\it Middle:} RV measurements, with best-fit instrument offsets
	and jitter terms included.  The expected scatter from starspots
	based on $v\sin i$ and the photometric modulation amplitude is of
	order 300m$\,$s$^{-1}$.
	{\it Bottom:}
	RV measurements phased to the orbital ephemeris of \pn.  The
	planet is not detected.  The black line shows a circular
	Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

{\bf George TODO: please describe the formal secondary line search in
more depth in this paragraph} We searched for secondary lines in the
CHIRON spectra by cross-correlating against a {\bf template of some
kind}.  This rules out lines with flux ratios of $\approx 2\%$, if the
lines are well-separated in velocity.  To derive the star's physical
parameters, we cross-correlated the template against {\bf something},
and used the {\bf \texttt{nameofcode}}.  We measured the radial
velocities through a least-squares deconvolution of the observed
spectra against the same synthetic template.  The resulting velocities
are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.

@@

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, {\bf
Rafael TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

Many of the exposures were taken in average or poor seeing conditions,
when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due to
uncorrected fiber-to-fiber cross-contamination.  For
analysis purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit, we assumed a restrictive prior on the period and
time of periapse, using the known ephemeris from the transit.  We then
fitted for the semi-amplitude, instrument offsets, and jitter
parameters.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:followup}.
